---
title: "report"
author: "Subinoy"
date: "16 March 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r, echo=FALSE}

library(RISmed)
library(rmarkdown)
search_topic <- 'selective serotonin reuptake inhibitors and autism'
search_query <- EUtilsSummary(search_topic, retmax=10000, mindate=2000,maxdate=2017)
```

# Search term used : "selective serotonin reuptake inhibitors and autism"
```{r, echo=FALSE}
summary(search_query)
#QueryId(search_query)
```

```{r, echo=FALSE, warning=FALSE}
tally <- array()
x <- 1
for (i in 2000:2017){
    Sys.sleep(1)
    r <- EUtilsSummary('selective serotonin reuptake inhibitors and autism', type='esearch',
                       db='pubmed', mindate=i, maxdate=i)
    tally[x] <- QueryCount(r)
    x <- x + 1
}

names(tally) <- 2000:2017
```

Maximum hits in a single year
```{r,echo=FALSE, fig.width=7, warning=FALSE}
max(tally)

barplot(tally, las=2, ylim=c(0,50), fig.width=7,
        main="selective serotonin reuptake inhibitors & autism")
```


```{r, echo=FALSE, warning=FALSE}
tally <- array()
x <- 1
for (i in 2000:2017){
    Sys.sleep(1)
    r <- EUtilsSummary('selective serotonin reuptake inhibitors and autism and brain', type='esearch',
                       db='pubmed', mindate=i, maxdate=i)
    tally[x] <- QueryCount(r)
    x <- x + 1
}

names(tally) <- 2000:2017
```

Maximum hits in a single year
```{r,echo=FALSE,fig.width=7, warning=FALSE}
max(tally)

barplot(tally, las=2, ylim=c(0,50), 
        main="selective serotonin reuptake inhibitors\
        & autism and brain")
```

```{r, echo=FALSE}

search_topic <- 'Metabolism of diazepam and selective serotonin re-uptake inhibitors in the brain'
search_query <- EUtilsSummary(search_topic, retmax=10000, mindate=2000,maxdate=2017)
```
## Search term: "Metabolism of diazepam and selective serotonin re-uptake inhibitors in the brain"
```{r diazepam0, echo=FALSE, fig.width=7, message=FALSE, warning=FALSE}
summary(search_query)
```
```{r, echo=FALSE, warning=FALSE}
tally <- array()
x <- 1
for (i in 2000:2017){
    Sys.sleep(1)
    r <- EUtilsSummary('Metabolism of diazepam and selective serotonin re-uptake inhibitors in the brain', type='esearch',db='pubmed', mindate=i, maxdate=i)
    tally[x] <- QueryCount(r)
    x <- x + 1
}

names(tally) <- 2000:2017
```
Maximum hits in a single year
```{r, echo=FALSE, fig.width=7, message=FALSE, warning=FALSE}
max(tally)

barplot(tally, las=2, ylim=c(0,50), 
        main="selective serotonin reuptake inhibitors\
        & autism and brain")
```


```{r, echo=FALSE}
search_topic <- 'Metabolism of diazepam and selective serotonin re-uptake inhibitors in the liver'
search_query <- EUtilsSummary(search_topic)
```

### Search term: "Metabolism of diazepam and serotonin specific re-uptake inhibitors in the liver"
```{r diazepam1, echo=FALSE, fig.width=7, message=FALSE, warning=FALSE}
summary(search_query)
```

```{r, echo=FALSE, warning=FALSE}
tally <- array()
x <- 1
for (i in 2000:2017){
    Sys.sleep(1)
    r <- EUtilsSummary('Metabolism of diazepam and selective serotonin re-uptake inhibitors in the liver', type='esearch',db='pubmed', mindate=i, maxdate=i)
    tally[x] <- QueryCount(r)
    x <- x + 1
}

names(tally) <- 2000:2017
```
Maximum hits in a single year
```{r, echo=FALSE, fig.width=7, message=FALSE, warning=FALSE}
max(tally)

barplot(tally, las=2, ylim=c(0,50), 
        main="Metabolism of diazepam and serotonin specific re-uptake\
inhibitors in the liver")
```


Metabolism of diazepam in the brain

```{r, echo=FALSE}
search_topic <- 'Metabolism of diazepam in the brain'
search_query <- EUtilsSummary(search_topic, retmax=10000, mindate=2000,maxdate=2017)
```

#### Search term: "Metabolism of diazepam in the brain"
```{r diazepam2, echo=FALSE, fig.width=7, message=FALSE, warning=FALSE}
summary(search_query)
```

```{r, echo=FALSE, warning=FALSE}
tally <- array()
x <- 1
for (i in 2000:2017){
    Sys.sleep(1)
    r <- EUtilsSummary('Metabolism of diazepam in the brain', type='esearch',db='pubmed', mindate=i, maxdate=i)
    tally[x] <- QueryCount(r)
    x <- x + 1
}

names(tally) <- 2000:2017
```
Maximum hits in a single year
```{r, echo=FALSE, fig.width=7, message=FALSE, warning=FALSE}
max(tally)

barplot(tally, las=2, ylim=c(0,100), 
        main="Metabolism of diazepam in the brain")
```