---
title: "t1"
author: "Subinoy"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: word_document
---

```{r, echo=FALSE}

library(RISmed)
library(rmarkdown)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r, echo=FALSE, include=FALSE}

library(RISmed)
library(rmarkdown)
search_topic <- 'selective serotonin reuptake inhibitors and autism'
s_name <- "SSRI_and_autism"
search_query <- EUtilsSummary(search_topic, retmax=10000, mindate=2000,maxdate=2017)
# get actual data from PubMed
records<- EUtilsGet(search_query)
# store it
pubmed_data <- data.frame('PMID'=search_query@PMID, 'Title'=ArticleTitle(records),
                          'Abstract'=AbstractText(records))
pubmed_data$Abstract <- as.character(pubmed_data$Abstract)
pubmed_data$Abstract <- gsub(",", " ", pubmed_data$Abstract, fixed = TRUE)
# write.csv(pubmed_data, file=paste(s_name, ".csv"))
```

# Search term used : "selective serotonin reuptake inhibitors and autism"

Article found
```{r, echo=FALSE, include=FALSE}
search_query@count


# summary(search_query)
#QueryId(search_query)
```
```{r, echo=FALSE, warning=FALSE}
tally <- array()
x <- 1
for (i in 2000:2017){
    Sys.sleep(1)
    r <- EUtilsSummary('selective serotonin reuptake inhibitors and autism', type='esearch',
                       db='pubmed', mindate=i, maxdate=i)
    tally[x] <- QueryCount(r)
    x <- x + 1
}

names(tally) <- 2000:2017
```

Maximum hits in a single year
```{r,echo=FALSE, fig.width=7, warning=FALSE, include=FALSE}
max(tally)

barplot(tally, las=2, ylim=c(0,50), fig.width=7,
        main="selective serotonin reuptake inhibitors & autism")
```


```{r, echo=FALSE, include=FALSE}

search_topic <- 'selective serotonin reuptake inhibitors and autism and brain'
s_name <- "2_SSRI_and_autism_brain"
search_query <- EUtilsSummary(search_topic, retmax=10000, mindate=2000,maxdate=2017)
# get actual data from PubMed
records<- EUtilsGet(search_query)
# store it
pubmed_data <- data.frame('PMID'=search_query@PMID, 'Title'=ArticleTitle(records),
                          'Abstract'=AbstractText(records))
pubmed_data$Abstract <- as.character(pubmed_data$Abstract)
pubmed_data$Abstract <- gsub(",", " ", pubmed_data$Abstract, fixed = TRUE)
write.csv(pubmed_data, file=paste(s_name, ".csv"))
``` 
## Search term used : "selective serotonin reuptake inhibitors and autism and brain" 
```{r, echo=FALSE, warning=FALSE, include=FALSE}
tally <- array()
x <- 1
for (i in 2000:2017){
    Sys.sleep(1)
    r <- EUtilsSummary('selective serotonin reuptake inhibitors and autism and brain', type='esearch',
                       db='pubmed', mindate=i, maxdate=i)
    tally[x] <- QueryCount(r)
    x <- x + 1
}

names(tally) <- 2000:2017
```

Maximum hits in a single year
```{r,echo=FALSE, warning=FALSE, include=FALSE}
max(tally)

barplot(tally, las=2, ylim=c(0,50), fig.width=7,
        main="selective serotonin reuptake inhibitors and autism and brain")

# end of 2nd
```

```{r, echo=FALSE, include=FALSE}
search_topic <- 'Metabolism of diazepam and selective serotonin re-uptake inhibitors in the brain'
s_name <- "3_Diazepam_SSRI_and_autism_brain"
search_query <- EUtilsSummary(search_topic, retmax=10000, mindate=2000,maxdate=2017)
# get actual data from PubMed
records<- EUtilsGet(search_query)
# store it
pubmed_data <- data.frame('PMID'=search_query@PMID, 'Title'=ArticleTitle(records),
                          'Abstract'=AbstractText(records))
pubmed_data$Abstract <- as.character(pubmed_data$Abstract)
pubmed_data$Abstract <- gsub(",", " ", pubmed_data$Abstract, fixed = TRUE)
write.csv(pubmed_data, file=paste(s_name, ".csv"))

```
### Search term: "Metabolism of diazepam and selective serotonin re-uptake inhibitors in the brain"

Article found
```{r , echo=FALSE, fig.width=7, message=FALSE, warning=FALSE, include=FALSE}
search_query@count
```
```{r, echo=FALSE, warning=FALSE, include=FALSE}
tally <- array()
x <- 1
for (i in 2000:2017){
    Sys.sleep(1)
    r <- EUtilsSummary('Metabolism of diazepam and selective serotonin re-uptake inhibitors in the brain', type='esearch',db='pubmed', mindate=i, maxdate=i)
    tally[x] <- QueryCount(r)
    x <- x + 1
}

names(tally) <- 2000:2017
```
Maximum hits in a single year
```{r, echo=FALSE, fig.width=7, message=FALSE, warning=FALSE, include=FALSE}
max(tally)

barplot(tally, las=2, ylim=c(0,50), 
        main="Metabolism of diazepam and selective serotonin re-uptake\ inhibitors in the brain")
# end of 3rd
```

```{r,  echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
search_topic <- ' Metabolism of diazepam in the brain'
s_name <- "4_diazepm_brain"
search_query <- EUtilsSummary(search_topic, retmax=10000, mindate=2000,maxdate=2017)
# get actual data from PubMed
records<- EUtilsGet(search_query)
# store it
pubmed_data <- data.frame('PMID'=search_query@PMID, 'Title'=ArticleTitle(records),
                          'Abstract'=AbstractText(records))
pubmed_data$Abstract <- as.character(pubmed_data$Abstract)
pubmed_data$Abstract <- gsub(",", " ", pubmed_data$Abstract, fixed = TRUE)
# write.csv(pubmed_data, file=paste(s_name, ".csv"))
```

#### Search term: "Metabolism of diazepam in the brain"

Article found
```{r , echo=FALSE, fig.width=7, message=FALSE, warning=FALSE, include=FALSE}
search_query@count
```
```{r, echo=FALSE, warning=FALSE, include=FALSE}
tally <- array()
x <- 1
for (i in 2000:2017){
    Sys.sleep(1)
    r <- EUtilsSummary('Metabolism of diazepam in the brain', type='esearch',db='pubmed', mindate=i, maxdate=i)
    tally[x] <- QueryCount(r)
    x <- x + 1
}

names(tally) <- 2000:2017
```
Maximum hits in a single year
```{r, echo=FALSE, fig.width=7, message=FALSE, warning=FALSE, include=FALSE}
max(tally)

barplot(tally, las=2, ylim=c(0,100), 
        main="Metabolism of diazepam in the brain")
# end of 4th
```

```{r,  echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
search_topic <- ' Metabolism of diazepam and selective serotonin reuptake inhibitors'
s_name <- "5_diazepm_SSRI"
search_query <- EUtilsSummary(search_topic, retmax=10000, mindate=2000,maxdate=2017)
# get actual data from PubMed
records<- EUtilsGet(search_query)
# store it
pubmed_data <- data.frame('PMID'=search_query@PMID, 'Title'=ArticleTitle(records),
                          'Abstract'=AbstractText(records))
pubmed_data$Abstract <- as.character(pubmed_data$Abstract)
pubmed_data$Abstract <- gsub(",", " ", pubmed_data$Abstract, fixed = TRUE)
write.csv(pubmed_data, file=paste(s_name, ".csv"))
```

### Search term: "Metabolism of diazepam and selective serotonin reuptake inhibitors"

Article found
```{r , echo=FALSE, fig.width=7, message=FALSE, warning=FALSE, include=FALSE}
search_query@count
```
```{r, echo=FALSE, warning=FALSE, include=FALSE}
tally <- array()
x <- 1
for (i in 2000:2017){
    Sys.sleep(1)
    r <- EUtilsSummary('Metabolism of diazepam and selective serotonin reuptake inhibitors', type='esearch',db='pubmed', mindate=i, maxdate=i)
    tally[x] <- QueryCount(r)
    x <- x + 1
}

names(tally) <- 2000:2017
```
Maximum hits in a single year
```{r, echo=FALSE, fig.width=7, message=FALSE, warning=FALSE,include=FALSE}
max(tally)

barplot(tally, las=2, ylim=c(0,50), 
        main="Metabolism of diazepam and \
        selective serotonin reuptake inhibitors")
# end of 5th
```


```{r,  echo=FALSE, message=FALSE, warning=FALSE}
search_topic <- ' Metabolism of diazepam and selective serotonin reuptake inhibitors in the brain'
s_name <- "6_diazepm_SSRI_brain"
search_query <- EUtilsSummary(search_topic, retmax=10000, mindate=2000,maxdate=2017)
# get actual data from PubMed
records<- EUtilsGet(search_query)
# store it
pubmed_data <- data.frame('PMID'=search_query@PMID, 'Title'=ArticleTitle(records),
                          'Abstract'=AbstractText(records))
pubmed_data$Abstract <- as.character(pubmed_data$Abstract)
pubmed_data$Abstract <- gsub(",", " ", pubmed_data$Abstract, fixed = TRUE)
write.csv(pubmed_data, file=paste(s_name, ".csv"))
```

### Search term: "Metabolism of diazepam and selective serotonin reuptake inhibitors in the brain"

Article found
```{r , echo=FALSE, fig.width=7, message=FALSE, warning=FALSE}
search_query@count
```
```{r, echo=FALSE, warning=FALSE}
tally <- array()
x <- 1
for (i in 2000:2017){
    Sys.sleep(1)
    r <- EUtilsSummary('Metabolism of diazepam and selective serotonin reuptake inhibitors in the brain', type='esearch',db='pubmed', mindate=i, maxdate=i)
    tally[x] <- QueryCount(r)
    x <- x + 1
}

names(tally) <- 2000:2017
```
Maximum hits in a single year
```{r, echo=FALSE, fig.width=7, message=FALSE, warning=FALSE,}
max(tally)

barplot(tally, las=2, ylim=c(0,50), 
        main="Metabolism of diazepam and \
        selective serotonin reuptake inhibitors in the brain")
# end of 6th
```